---
title: Homework Assignment 1
author: Matthew Onimus
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
  toc: true
number_sections: true
toc_float: true
---
  
<div style="margin-bottom:100px;">
  
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

$~$

# Complete the following :

## load the tidyverse:

I also loaded in the `here` and `DBI` packages to make filepaths and database connections easier.

```{r}
library(tidyverse)
library(here)
library(DBI)
```


## Connect to the database:

**I have changed the below chunk to align with current dbplyr functions and DBI connection strings.  I have also used the `here` package to reference the correct path.**

```{r}

# NHANES_DB <- src_sqlite(
#   #TODO , 
#   create = FALSE)

con <- DBI::dbConnect(RSQLite::SQLite(), here("NHANES_DB.db"))


```

Create a list of tables called `NHANES_Tables`.  I have made this a little easier using the DBI package.

```{r}

NHANES_Tables <- dbListTables(con)

# NHANES_Tables <-  src_tbls(#TODO) [! src_tbls(#TODO) %in% c("sqlite_stat1" , 'sqlite_stat4') ]

NHANES_Tables

```

There are `r length(NHANES_Tables)` tables in the NHANES database.

```{r}

NHANES_table_helper <- function(Table_Name){
  url_link <- paste0('https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/',Table_Name,'_J.htm')
  return(url_link)
}

```



```{r}

# i typically try not to reference global variables in a function call, I have updated the below function to take all the required arguments.  Also updated the first cat in the else statement to be a warning 

Open_NHANES_table_help <- function(Table_Name, NHANES_Tables){
  
  if(Table_Name %in% NHANES_Tables){
    return(
      NHANES_table_helper(Table_Name)
      )
  } else {
    ln1 <- paste0("ERROR : ", Table_Name, " is not a valid table name! \n")
    ln2 <- 'Please Choose one of : \n'
    ln3 <- NHANES_Tables
    warning(ln1)
    cat(ln2)
    cat(ln3)
  }
}

# added the browseURL code to open the returned url
browseURL(Open_NHANES_table_help('TCHOL', NHANES_Tables))

# error checking test
Open_NHANES_table_help('TCOL', NHANES_Tables)


```

----------------------------------------------------------------------------
  
$~$

# Code Appendix

$~$

$~$

```{r show-code, ref.label=setdiff(all_labels(),c('setup')), echo = TRUE, eval=FALSE}

```
